Relocating a Cluster of Earthquakes Using a Single Seismic Station

### 2013-01-04 paper2/paper2.tex
this is the version submitted after responding to the first set of comments from the Editorial office

%\bibliographystyle{agufull08} % Uncomment when generating bibliography
\usepackage{timet}
\usepackage[dvips]{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{rotating}
\usepackage{natbib}
\usepackage{lineno}
%\usepackage{titlesec}
\linenumbers

@@

\vspace{2em}
\begin{centering}
\section*{Data and Resources}
\end{centering}
We thank the Northern California Earthquake Data Center (NCEDC) for
providing the Calaveras data and the Northern California Seismic
Network (NCSN), U.S. Geological Survey, Menlo Park and Berkeley
Seismological Laboratory, University of California, Berkeley for
contributing it to the NCEDC. The waveforms can be downloaded from
http://www.ncedc.org/ncedc/access.html (last accessed August 2012). 
We also acknowledge Felix
Waldhauser and William Ellsworth, the authors of the openly
available Double Difference location algorithm, hypoDD which can be
downloaded from http://www.ldeo.columbia.edu/~felixw/hypoDD.html
(last accessed August 2012).
The International Sesimological Centre can be found at 
http://www.isc.ac.uk/ (last accessed December 2012).
The National Earthquake
Information
Center catalogue can be accessed from \\
http://earthquake.usgs.gov/earthquakes/eqarchives/epic/
(last accessed December 2012).

@@

\clearpage
%\begin{centering}
%\section*{Figure Captions}
%\end{centering} 
%%=======================================================================================

%Figure 1
\noindent\includegraphics[width = 20pc]{Figure1_c.eps} \\
\textbf{Figure 1:}

@@

%Figure 2
\clearpage
\noindent\includegraphics[width = 20pc]{Figure2_c.eps} \\
\textbf{Figure 2:}

@@

% Figure 3
\clearpage
\noindent\includegraphics[width=20pc]{Figure3_c.eps} \\
\textbf{Figure 3:}

@@

% Figure 4
\clearpage
\noindent\includegraphics[width=20pc]{Figure4_c.eps} \\
\textbf{Figure 4:}

@@

% Figure 5
\clearpage
\noindent\includegraphics[width=20pc]{Figure5.eps} \\
\textbf{Figure 5:}

%%=======================================================================================
% Figure 6
\clearpage
\includegraphics{Figure6_bw.eps} \\
\textbf{Figure 6:}

@@

% Figure 7
\clearpage
\noindent\includegraphics[width=20pc]{Figure7.eps} \\
\textbf{Figure 7:}

@@

%Figure 8
\textbf{Figure 8:} \noindent\includegraphics[angle=90,height = 50pc]{Figure8_bw.eps} \\
%\noindent\includegraphics[width= 50pc]{Figure8_bw.eps} \\

%%=========================================================================
% Figure 9
\noindent\includegraphics[height = 25pc]{Figure9_bw.eps} \\
\textbf{Figure 9:}

@@

%Figure 10
\clearpage
\noindent\includegraphics[width=20pc]{Figure10_c.eps} \\
\textbf{Figure 10:}

@@

% Figure 11
\clearpage
\includegraphics{Figure11_bw.eps} \\
\textbf{Figure 11:}

@@

% Figure 12
\clearpage
\noindent\includegraphics[width = 20pc]{Figure12_c.eps} \\
\textbf{Figure 12:}

@@

% Figure 13
\clearpage
\includegraphics{Figure13_bw.eps} \\
\textbf{Figure 13:}

>>>>

%\bibliographystyle{agufull08} % Uncomment when generating bibliography
%\usepackage{timet}
\usepackage[dvips]{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{rotating}
\usepackage{natbib}
\usepackage{lineno}
%\usepackage{titlesec}
\linenumbers

@@

\vspace{2em}
\begin{centering}
\section*{Data and Resources}
\end{centering}
We thank the Northern California Earthquake Data Center (NCEDC) for
providing the Calaveras data and the Northern California Seismic
Network (NCSN), U.S. Geological Survey, Menlo Park and Berkeley
Seismological Laboratory, University of California, Berkeley for
contributing it to the NCEDC. The waveforms can be downloaded from \\
http://www.ncedc.org/ncedc/access.html (last accessed August 2012). 
We also acknowledge Felix
Waldhauser and William Ellsworth, the authors of the openly
available Double Difference location algorithm, hypoDD which can be
downloaded from \\
http://www.ldeo.columbia.edu/~felixw/hypoDD.html
(last accessed August 2012).
The International Sesimological Centre can be found at \\
http://www.isc.ac.uk/ (last accessed December 2012).
The National Earthquake
Information
Center catalogue can be accessed from \\
http://earthquake.usgs.gov/earthquakes/eqarchives/epic/
(last accessed December 2012).

@@

%\clearpage
%\begin{centering}
%\section*{Figure Captions}
%\end{centering} 
%%=======================================================================================

%Figure 1
%\noindent\includegraphics[width = 20pc]{Figure1_c.eps} \\
%\textbf{Figure 1:}

@@

%Figure 2
%\clearpage
%\noindent\includegraphics[width = 20pc]{Figure2_c.eps} \\
%\textbf{Figure 2:}

@@

% Figure 3
%\clearpage
%\noindent\includegraphics[width=20pc]{Figure3_c.eps} \\
%\textbf{Figure 3:}

@@

% Figure 4
%\clearpage
%\noindent\includegraphics[width=20pc]{Figure4_c.eps} \\
%\textbf{Figure 4:}

@@

% Figure 5
%\clearpage
%\noindent\includegraphics[width=20pc]{Figure5.eps} \\
%\textbf{Figure 5:}

%%=======================================================================================
% Figure 6
%\clearpage
%\includegraphics{Figure6_bw.eps} \\
%\textbf{Figure 6:}

@@

% Figure 7
%\clearpage
%\noindent\includegraphics[width=20pc]{Figure7.eps} \\
%\textbf{Figure 7:}

@@

%Figure 8
%\textbf{Figure 8:} \noindent\includegraphics[angle=90,height = 50pc]{Figure8_bw.eps} \\
%\noindent\includegraphics[width= 50pc]{Figure8_bw.eps} \\

%%=========================================================================
% Figure 9
%\noindent\includegraphics[height = 25pc]{Figure9_bw.eps} \\
%\textbf{Figure 9:}

@@

%Figure 10
%\clearpage
%\noindent\includegraphics[width=20pc]{Figure10_c.eps} \\
%\textbf{Figure 10:}

@@

% Figure 11
%\clearpage
%\includegraphics{Figure11_bw.eps} \\
%\textbf{Figure 11:}

@@

% Figure 12
%\clearpage
%\noindent\includegraphics[width = 20pc]{Figure12_c.eps} \\
%\textbf{Figure 12:}

@@

% Figure 13
%\clearpage
%\includegraphics{Figure13_bw.eps} \\
%\textbf{Figure 13:}
